Type-Safe Modular Parsing

### 2016-10-31 paper/sections/CaseStudy.tex
Rearrange the table and the graph

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{depGraph}
    \caption{Dependency graph of all calculi and components}
    \label{fig:dependency}
\end{figure}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|r|}
        \hline
        \bfseries Calculus Name & \bfseries Ilya's & \bfseries Ours & \bfseries (+/-)\%
        \csvreader{../Scala/sloc.csv}{}
        {\\\hline \csvcoli & \csvcolii & \csvcoliii & \csvcoliv}
        %    \csvautotabular{../Scala/sloc.csv}
        \\\hline
    \end{tabular}
    \caption{Comparison of SLOC and execution time}
    \label{tab:comparison}
\end{table}

Table \ref{tab:comparison} shows the comparison result.

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{resources/depGraph.pdf}
    \caption{Dependency graph of all calculi and components}
    \label{fig:dependency}
\end{figure}

@@

\begin{table}
    \centering
    \input{resources/CaseStudyTable.tex}
    \caption{Comparison of SLOC and execution time}
    \label{tab:comparison}
\end{table}

Table \ref{tab:comparison} shows data of the comparison. The overall result of SLOC comparison is that 60\% of code in total is reduced using our library. That is because the code of some common syntax structures such as variable, lambda abstraction, etc., is reused several times in the whole project. We can see that the first two calculi \lstinline{Arith} and \lstinline{Untyped} we do worse than Ilya's implementation, because in such two cases we do not reuse any existing components. But in each of the following 16 calculi, we can compose our syntax definition, parser and pretty printer from extending reusable components, resulting considerably code reduction.
